---
title: "Aviation Safety Data : Dataset Exploration & Analysis"
author: "R Sangole"
date: "Feb 25 2018"
output: 
  html_notebook: 
    highlight: zenburn
    theme: cerulean
    toc_float: yes
    toc: true
    
---

```{r include=FALSE}
options(knitr.table.format = "html") 
library(knitr)
library(kableExtra)
```

# What's the Objective?

* This is the dataset used for the SIAM 2007 Text Mining competition. 
* This competition focused on developing text mining algorithms for document classification. 
* The documents in question were aviation safety reports that documented one or more problems that occurred during certain flights. 
* The goal was to label the documents with respect to the types of problems that were described. This is a subset of the Aviation Safety Reporting System (ASRS) dataset, which is publicly available.

The data is obtained from [this link](https://c3.nasa.gov/dashlink/resources/138/).

# Quick Look

The training data looks like this:

```{r}
head(training_data,2) %>% kable(align = c('c','l')) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The training data labels look like this:

```{r}
head(training_labels,2)
```

The size of the dataset is large, a total of [`r dim(training_data)`], while that of the label dataset is [`r dim(training_labels)`].



```{r}
(colSums(training_labels)+21519) %>% tail(-1) %>% as.data.frame() %>% rownames_to_column() %>% mutate(rowname=reorder(rowname,.)) %>% ggplot(aes(rowname,.))+geom_col()+coord_flip()
```

```{r}
training_labels %>% mutate(b_and_s = ifelse(cat_b==1 & cat_s==1,T,F)) %>% count(b_and_s)
```

```{r}
set.seed(1)
training_labels %>% 
    mutate(b_and_s = ifelse(cat_b==1 & cat_s==1,T,F)) %>% 
    filter(!b_and_s) %>% 
    sample_n(1e3) -> sub_train_labels
```

